---
title: "Initial EDA"
subtitle: "STAT 301-3: Data Science III"
output: 
  html_document: 
    code_folding: hide
date: '2022-05-01'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r,message=FALSE, warning=FALSE}
library(skimr)
library(tidyverse)
library(patchwork)
```

### 1. Initial overview of data

```{r}
shop_dat <- 
  read_csv("data/unprocessed/online_shoppers_intention.csv") %>% 
  janitor::clean_names()
```

#### Date Collection & Cleaning

We obtained the data from University of California Irvine's machine learning repository. The dataset was collected by a faculty researcher and information technology specialist in Turkey from an online bookstore built on an osCommerce platform.

No cleaning was needed for the EDA.

#### Initial Skim

(Number of observations (n), number of features (p), missingness)

```{r}
skim(shop_dat)
```

### 2. Essential Findings (Important or Interesting)

#### Univariate investigation of response variable: Revenue

```{r}
ggplot(shop_dat, aes(revenue)) +
  geom_bar()
```

#### Univariate investigation of important predictor variables

```{r}
ggplot(shop_dat, aes(visitor_type)) +
  geom_bar()

ggplot(shop_dat, aes(month)) +
  geom_bar()

ggplot(shop_dat, aes(weekend)) +
  geom_bar()

ggplot(shop_dat, aes(special_day)) +
  geom_bar()

ggplot(shop_dat, aes(bounce_rates)) +
  geom_histogram()

ggplot(shop_dat, aes(exit_rates)) +
  geom_histogram()
```

#### Relationships between Revenue & predictor variables

```{r}
p1 <- ggplot(data = shop_dat, mapping = aes(x = revenue)) +
  geom_bar(mapping = aes(fill = visitor_type)) + 
  ggtitle("Revenue on visitor type") + 
  xlab("Revenue") + 
  ylab("Visitors") + 
  theme(legend.position = "bottom")

p2 <- ggplot(data = shop_dat, mapping = aes(x = revenue)) +
  geom_bar(mapping = aes(fill = weekend)) + 
  ggtitle("Revenue on weekend status") + 
  xlab("Revenue") + ylab("Visitors") + 
  theme(legend.position = "bottom")

(p1 + p2)
```

#### Relationships among predictor variables

```{r}
# informational duration & product related duration
shop_dat %>% 
  ggplot(aes(x = informational_duration, y = product_related_duration)) +
  geom_point(alpha = 0.5) +
  geom_smooth()

# exit rate & bounce rate
ggplot(data = shop_dat, mapping = aes(x = bounce_rates, y = exit_rates)) +
  geom_point(mapping = aes(color = revenue)) + geom_smooth(se = TRUE, alpha = 0.5) +
  theme_light() + 
  ggtitle("Relationship between Exit Rates and Bounce Rates") + 
  xlab("Exit Rates") + 
  ylab("Bounce Rates")
```

### 3.Secondary Findings

#### Other Explorations

(Standard variable explorations for the domain area that are unsurprising and mainly conducted out of convention.)

Standard explorations of variables that are included in our dataset:

-   "Our research has shown that, even by using the most basic information (e.g. **event type**), it is possible to reliably predict conversion based on simple and lightweight features in a variety of scenarios." Event types include the following: "*page view* is triggered when the final user loads any page in the website; a*detail* event is triggered when the user visits a specific product page, i.e. a page displaying one particular product; an*add/remove* event is triggered when a product is added/removed from the cart; a*purchase* event is triggered when the user actually buys the products in the cart; finally, a *click* event is triggered when some results from a search query are clicked e.g. user searches for "shoes" using the e-commerce search bar, several products are returned and the user clicks on the second product triggering a *click* event."
    -   Requena, B., Cassani, G., Tagliabue, J. *et al.* Shopper intent prediction from clickstream e-commerce data with minimal browsing information. *Sci Rep* **10,** 16983 (2020). <https://doi.org/10.1038/s41598-020-73622-y>
-   "We found that "**Session Duration**" is the most important feature that gives critical signal for predicting users' purchase intention."
    -   Esmeli, R., Bader-El-Den, M. & Abdullahi, H. Towards early purchase intention prediction in online session based retailing systems. *Electron Markets* **31,** 697--715 (2021). <https://doi.org/10.1007/s12525-020-00448-x>
-   The greatest predictors of generating revenue are: "**new visitor**, **visitors who has low bounce rate**, **month sales in November and May**, **visitor who spent more time in product related.**"
    -   Muda, Muhammad & Iswari, Radha & Ahsan, Muhammad. (2020). Prediction of Online Shopper's Purchasing Intention Using Binary Logistic Regression, Decision Tree, and Random Forest. 10.13140/RG.2.2.16567.55209.

Standard explorations of variables that are not included in our dataset (this information can help us indirectly):

-   "It is found that **online trust** is an important factor affecting consumers' online search intention, and the most important factor for consumers' online **purchase intention is their perceived benefits of online shopping**. At the same time, there is a positive relationship between **online search intention** and purchase intention."
    -   Deng W, Su T, Zhang Y, Tan C. Factors Affecting Consumers' Online Choice Intention: A Study Based on Bayesian Network. *Front Psychol*. 2021;12:731850. Published 2021 Oct 20. <doi:10.3389/fpsyg.2021.731850>
-   "**Subjective norm** and **perceived usefulness** significant positively influence online purchase intention."
    -   Jin Lim, Abdullah Osman, Shahrul Nizam Salahuddin, Abdul Rahim Romle, Safizal Abdullah, Factors Influencing Online Shopping Behavior: The Mediating Role of Purchase Intention, Procedia Economics and Finance, Volume 35, 2016, Pages 401-410, ISSN 2212-5671, [https://doi.org/10.1016/S2212-5671(16)00050-2.](https://doi.org/10.1016/S2212-5671(16)00050-2.)

#### Other Findings

(Findings that don't seem interesting or important, but show some potential.)

-   " '**Min Popularity**' feature that indicates the value of minimum popularity of the browsed items in the session is found as having the lowest importance to classify users' purchase intention."

    -   Esmeli, R., Bader-El-Den, M. & Abdullahi, H. Towards early purchase intention prediction in online session based retailing systems. *Electron Markets* **31,** 697--715 (2021). <https://doi.org/10.1007/s12525-020-00448-x>
